%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% baposter Portrait Poster
% LaTeX Template
% Version 1.0 (15/5/13)
%
% Created by:
% Brian Amberg (baposter@brian-amberg.de)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\title{GAME220 - Assignment X}
\documentclass[archE1,portrait]{baposter}

%841mm x 1189mm
\usepackage[font=small,labelfont=bf]{caption} % Required for specifying captions to tables and figures
\usepackage{booktabs} % Horizontal rules in tables
\usepackage{relsize} % Used for making text smaller in some places
\usepackage[urlcolor  = blue]{hyperref}
\usepackage{outlines}
\usepackage{tabularx}

\graphicspath{{figures/}} % Directory in which figures are stored

\definecolor{bordercol}{RGB}{5,2,82} % Border color of content boxes
\definecolor{headercol1}{RGB}{5,2,82} % Background color for the header in the content boxes (left side)
\definecolor{headercol2}{RGB}{5,2,82} % Background color for the header in the content boxes (right side)
\definecolor{headerfontcol}{RGB}{255,255,255} % Text color for the header text in the content boxes
\definecolor{boxcolor}{RGB}{255,255,255} % Background color for the content in the content boxes

\begin{document}
\newgeometry{top=.4in, bottom=.4in, left=.55in,right=.55in}
\background{ % Set the background to an image (background.pdf)

}

\begin{poster}
{
	grid=false,
	borderColor=bordercol, % Border color of content boxes
	headerColorOne=headercol1, % Background color for the header in the content boxes (left side)
	headerColorTwo=headercol1, % Background color for the header in the content boxes (right side)
	headerFontColor=headerfontcol, % Text color for the header text in the content boxes
	boxColorOne=boxcolor, % Background color for the content in the content boxes
	headershape=roundedright, % Specify the rounded corner in the content box headers
	headerfont=\Large\sf\bf, % Font modifiers for the text in the content box headers
	textborder=rectangle,
	background=user,
	headerborder=open, % Change to closed for a line under the content box headers
	boxshade=plain,
	columns=4
}
{}
%
%----------------------------------------------------------------------------------------
%	TITLE AND AUTHOR NAME
%----------------------------------------------------------------------------------------
%
%\vspace{2em}
{
%\newline
\sf\bf Dungeon Disaster} % Poster title
{\vspace{.5em} Kyle Salitrik\\ % Author names
% {\smaller kps168@psu.edu}\\
% %\vspace{1em}
% \underline{\url{http://moca.usc.edu}}
%\vspace{1em}
} % Author email addresses
%



%----------------------------------------------------------------------------------------
%	GENRES
%----------------------------------------------------------------------------------------

\headerbox{Genres}{name=game_genre,span=4,column=0}
{ 
	\begin{tabularx}{\textwidth}{ X | X }
	\underline{\textbf{Story:}} Fantasy, Medieval & \underline{\textbf{Gameplay:}} Top-down RPG
	\end{tabularx}
	\vspace*{-.6\baselineskip}
}


%----------------------------------------------------------------------------------------
%	Intended Audience
%----------------------------------------------------------------------------------------
\headerbox{Intended Audience}{name=intended_audience,span=3,column=0, below=game_genre}
{ 
	Hardcore mobile gamers
}

%----------------------------------------------------------------------------------------
%	Intended Platform
%----------------------------------------------------------------------------------------
\headerbox{Platforms:}{name=intended_platform,span=1,column=3, below=game_genre}
{ 
	PC \& Console
}

%----------------------------------------------------------------------------------------
%	Summary
%----------------------------------------------------------------------------------------

\headerbox{Game Summary}{name=summary,column=0,row=0, span=4, below=intended_audience}
{
	\quad Using wit, persistence, and puzzle-solving skills, players crawl through dungeons defeating enemies along the way in an old-school, top-down style RPG.
}

%----------------------------------------------------------------------------------------
%	Narrative
%----------------------------------------------------------------------------------------

\headerbox{Narrative Summary}{name=narrative,column=0,row=0, span=4, below=summary}
{
	\quad Players are trapped in a dungeon during an earthquake and must fight their way out to freedom by defeating monsters and solving puzzles to open the next level above them.
}

%----------------------------------------------------------------------------------------
%	Game Outline
%----------------------------------------------------------------------------------------

\headerbox{Gameplay Outline}{name=outline,column=0,row=0, span=4, below=narrative}
{
	\quad Players are tasked with solving a puzzle in order to remove rubble from the exit of the current level of the dungeon to the level above, all the while being thwarted by endless waves of skeletons, zombies and other enemies. Puzzle solutions range from finding a button to press to destroying the most mundane objects such as a chair. As the game progresses, more members will be added to the team, up to 6 characters that the players can control to solve increasingly complex puzzles.
	
	\quad Throughout their journey player's characters will level up and gain new equipment as the standard RPG trope, but changing a characters equipment will change their class. Each player's level is tied to the character and not their individual classes, so switching on the fly is a breeze and makes your team more adaptable as you encounter harder tasks.
	
}

%----------------------------------------------------------------------------------------
%	USP
%----------------------------------------------------------------------------------------

\headerbox{Mechanics Breakdown}{name=USPs,span=4,column=0,below=outline}
{ 
	\begin{outline}
		\1 Playable Characters
			\2 Each character has their own level and equipment
			\2 Equipment determines character class
				\3 Ex: Equipping a staff will make the character a mage, while equipping a sword will turn them into a warrior.
			\2 When a character levels up their stats increase automatically and reallocate when they change their class in order to prevent players from shooting themselves in the foot.
		\1 Dungeon Levels
			\2 Each level will have a unique mechanic in puzzle solving in order to progress to the next level.
			\2 Each level will have it's own set of enemies that will spawn in order to vary gameplay.
			\2 Enemies will adapt to the player character's highest leveled character.
	\end{outline}
}
\end{poster}

\end{document}
